Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv("dataSets/pseudo_facebook.tsv", sep='\t')
qplot(age,friend_count, data=pf)

```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x=age, y=friend_count), data=pf) + 
  geom_jitter(alph = 1/20) +
  xlim(c(13,90))

summary(pf$age)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x=age, y=friend_count), data=pf) + 
  geom_jitter(alph = 1/20) +
  xlim(c(13,90))

```

#### What do you notice in the plot?
Response:
Most are still under 25. Cluster at around 69.
***

### Coord_trans()
Notes:
  


```{r Coord_trans()}
# without jitter
ggplot(aes(x=age, y=friend_count), data=pf) + 
    geom_point(alph = 1/20) +
    xlim(c(13,90)) +
  coord_trans(y="sqrt")

ggplot(aes(x=age, y=friend_count), data=pf) + 
    geom_point(alph = 1/20, position = position_jitter(h=0)) +
    xlim(c(13,90)) +
  coord_trans(y="sqrt")

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
library(ggplot2)
pf <- read.csv("dataSets/pseudo_facebook.tsv", sep='\t')

myplot <- ggplot(aes( x=age, y = friendships_initiated), data = pf) + xlim(c(13,90))
myplot + geom_jitter(alpha = 1/20)

myplot + geom_point(alpha = 1/20) + coord_trans(y="sqrt")

myplot + geom_point(alpha = 1/10, position = 'jitter')

myplot + geom_jitter(alpha = 1/10, position = position_jitter(h = 0))

```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}


library(dplyr)
age_groups <- group_by(pf, age)
pf.fc_by_age <- summarise(age_groups,
          friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n=n())
pf.fc_by_age <- arrange(pf.fc_by_age, age)
head(pf.fc_by_age)


pf.fc_by_age <- pf %>% 
  group_by(age) %>% 
  summarise(friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n=n()) %>% 
  arrange(age)


head(pf.fc_by_age, 20)

```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x = age , y = friend_count_mean), data = pf.fc_by_age) +
  geom_line() + xlim(c(13,90))
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}



```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(quantile(pf$age, .95), quantile(pf$friend_count, .95), method = "pearson")

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response: -0.02740737

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(                 , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
ggplot(pf, aes(x= likes_received, y= www_likes_received))+geom_point(position = "jitter", alpha = 1/10)+xlim(c(0,quantile(pf$likes_received, .95)))+ylim(c(0,quantile(pf$www_likes_received, .95))) +
  geom_smooth(method = "lm", color = "red")
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}


```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
cor.test(pf$likes_received, pf$www_likes_received)
```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
data(Mitchell)
```

Create your plot!

```{r Temp vs Month}
ggplot(Mitchell, aes(x = Temp, y = Month)) + geom_point()

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.
guessed: 0
b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
cor.test(Mitchell$Month, Mitchell$Temp,method = "pearson")

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(Mitchell, aes(y = Temp, x = Month)) + geom_point() + scale_x_discrete(breaks = seq(0, max(Mitchell$Month), 12))
```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

