Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
pf <- read.delim("~/Rprojects/udacityEDA/pseudo_facebook.tsv")
qplot(pf$friend_count)

```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
install.packages('ggplot2')
library(ggplot2)
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}

```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}

```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}

```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}

```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
Notes:

```{r Tenure}
qplot(x=tenure/365, data=pf, binwidth=.5, color=I("black"), fill=I('#099DD9'))

```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}

```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
qplot(data=pf, x=age, binwidth=2, xlab = "Age", ylab= "count") +
  scale_x_continuous(limits = c(10,100), breaks=c(0,21,35,40,50,63,70,80,90))

```

***

### User Ages
Notes:

```{r User Ages}

```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}
histo1 <- qplot(x=friend_count,data=pf)
histo.log <- histo1 + scale_x_log10()
histo.sqrt <- histo1 + scale_x_sqrt()
grid.arrange(histo1, histo.log,histo.sqrt,ncol=1)

```

***


### Frequency Polygons

```{r Frequency Polygons}


```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
qplot(www_likes, data=subset(pf,!is.na(gender)), geom="freqpoly", color = gender) + scale_x_continuous() + scale_x_log10()

by(pf$www_likes, pf$gender, sum)

```


***

### Box Plots
Notes:

```{r Box Plots}
qplot(geom="boxplot", data = subset(pf, !(is.na(gender))), y=friend_count, x =gender)

```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
qplot(geom="boxplot", data = subset(pf, !(is.na(gender))), y=friend_count, x =gender, ylim=c(0,1000))

qplot(geom="boxplot", data = subset(pf, !(is.na(gender))), y=friend_count, x =gender) + scale_y_continuous(limits=c(0,1000))

qplot(geom="boxplot", data = subset(pf, !(is.na(gender))), y=friend_count, x =gender) + coord_cartesian(ylim=c(0,1000))

```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}
mobile.check.in <- NA
pf$mobile.check.in <- ifelse(pf$mobile_likes > 0 , 1, 0)
pf$mobile.check.in  <- factor(pf$mobile.check.in)
summary(pf$mobile.check.in)
length(pf[,mobile.check.in==1])/length(pf$mobile.check.in)
        
        
```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!